---
classoption: landscape
output: pdf_document
params:
  invoiceNumber: 1000086-1022I-6857
---

```{r setup, include=FALSE}
require(lubridate)
library(dplyr)
library(RCurl)
library(jsonlite)
library(countrycode)
library(knitr)

data <- getURL(
  paste(
    "guest:guest@localhost:8080/opencrx-bpi-CRX/org.opencrx.application.bpi1/provider/CRX/segment/Standard/exporter/SalesContractExporter/file/invoice.json?param1=INVOICE&param2=", 
    params$invoiceNumber, 
    sep=""
  )
)
invoice <- fromJSON(data)

```

# INVOICE `r invoice$contractNumber`

**To:**

~~~~~~~
`r invoice$shippingAddress$postalAddressLine0`                  
`r invoice$shippingAddress$postalAddressLine1`
`r invoice$shippingAddress$postalStreet0`
`r invoice$shippingAddress$postalStreet1`
`r invoice$shippingAddress$postalCode` `r invoice$shippingAddress$postalCity`
`r countrycode(invoice$shippingAddress$postalCountry,"iso3n","country.name")`
~~~~~~~

**Date:** `r as.Date(invoice$activeOn, "%Y%m%d")`

**Summary:** `r invoice$name`.

```{r, echo=FALSE}
knitr::kable(invoice$positions)
```

**Total Amount:** `r sprintf("%5.2f", invoice$totalAmount, digits=2)`

**Total Tax:** `r sprintf("%5.2f", invoice$totalTaxAmount, digits=2)`
